RDF Validation Requirements - Evaluation and Logical Underpinning

### 2015-05-15 paper/RDF validation requirements/RDF validation requirements.tex
evaluation

\subsection{Class-Specific Irreflexive Object Properties*}

@@

\ms{Define Order} corresponds to the requirements
\ms{R-121-SPECIFY-ORDER-OF-RDF-} \ms{RESOURCES} and
\ms{R-217-DEFINE-ORDER-FOR-FORMS/DISPLAY}.
With this constraint objects of object properties can be ordered as well as literals of data properties and objects of object properties.

@@

\section{Default Values*}

@@

*Property Domain & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
*Property Range & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\

@@

*Existential Quantification & \ding{55} & $\checkmark$ & \ding{55} & $\sim$ & $\sim$ & $\checkmark$ \\
*Universal Quantification & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\

@@

Primary Key Properties & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\

@@

Define Order & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\

@@

\begin{evaluation-overall}
Context-Specific Valid Classes & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Context-Specific Valid Properties & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Default Values* & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ & \ding{55} & $\checkmark$ \\
Mathematical Operations & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Language Tag Matching & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Language Tag Cardinality & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Whitespace Handling & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
HTML Handling & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Conditional Properties & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Recommended Properties & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Handle RDF Collections & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Value is Valid for Datatype & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Exploiting Class/Property Specialization Ontology Axioms & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
*Cardinality Shortcuts & \ding{55} & $\checkmark$ & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
Aggregations & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
\end{evaluation-overall}

@@

*Property Domain & $\checkmark$ & $\sim$ & $\checkmark$ \\ 
*Property Range & $\checkmark$ & $\sim$ & $\checkmark$ \\ 

@@

*Existential Quantification & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
*Universal Quantification & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  

@@

Primary Key Properties & $\checkmark$ & $\sim$ & $\checkmark$ \\ 

@@

Define Order & $\checkmark$ & $\checkmark$ & \ding{55} \\ 

@@

\begin{evaluation-generic}
Context-Specific Valid Classes & \ding{55} & $\checkmark$ & \ding{55} \\   
Context-Specific Valid Properties & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
Default Values* & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
Mathematical Operations & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
Language Tag Matching & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
Language Tag Cardinality & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
Whitespace Handling & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
HTML Handling & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
Conditional Properties & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
Recommended Properties & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
Handle RDF Collections & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
Value is Valid for Datatype & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
*Exploiting Class/Property Specialization Ontology Axioms & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
*Cardinality Shortcuts & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
Aggregations & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
\end{evaluation-generic}

@@

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lcc@{}}
           & \multicolumn{2}{c}{\textbf{Dependency}}
    \\  \cmidrule{2-3}
    \\       \textbf{Constraint Types}
           & \rot{\emph{CWA}}
           & \rot{\emph{UNA}}
    \\ \midrule
		*Subsumption & $\checkmark$ & $\checkmark$ \\
		*Class Equivalence & $\checkmark$ & $\checkmark$ \\
		*Sub Properties & $\checkmark$  & $\checkmark$ \\
		*Property Domain & $\checkmark$ & $\checkmark$ \\
		*Property Range & $\checkmark$ & $\checkmark$ \\
		*Inverse Object Properties & $\checkmark$ & $\checkmark$ \\
		*Symmetric Object Properties & $\checkmark$ & $\checkmark$ \\
		*Asymmetric Object Properties & \ding{55} & \ding{55} \\
		*Reflexive Object Properties & $\checkmark$ & $\checkmark$ \\
		*Irreflexive Object Properties & \ding{55} & \ding{55} \\
		Disjoint Properties & \ding{55} & \ding{55} \\
		Disjoint Classes & \ding{55} & \ding{55} \\
		Context-Sp. Property Groups & $\checkmark$ & $\checkmark$ \\
		Context-Sp. Inclusive OR of P. & $\checkmark$ & $\checkmark$ \\
		Context-Sp. Inclusive OR of P. Groups & $\checkmark$ & $\checkmark$ \\
		Recursive Queries & \ding{55} & \ding{55} \\
		Individual Inequality & \ding{55} & \ding{55} \\
		*Equivalent Properties & $\checkmark$ & $\checkmark$ \\
		Property Assertions & $\checkmark$ & $\checkmark$ \\
		Data Property Facets & \ding{55} & \ding{55} \\
		Literal Pattern Matching & \ding{55} & \ding{55} \\
		Negative Literal Pattern Matching & \ding{55} & \ding{55} \\
		*Object Property Paths & $\checkmark$ & $\checkmark$ \\
		*Intersection & $\checkmark$ & $\checkmark$ \\
		*Disjunction & $\checkmark$ & $\checkmark$ \\
		*Negation & \ding{55} & $\checkmark$ \\
		*Existential Quantification & $\checkmark$ & \ding{55} \\
		*Universal Quantification & \ding{55} & $\checkmark$ \\
		*Minimum Unqualified Cardinality & $\checkmark$ & $\checkmark$ \\
		*Minimum Qualified Cardinality & $\checkmark$ & $\checkmark$ \\
		*Maximum Unqualified Cardinality & \ding{55} & $\checkmark$ \\
		*Maximum Qualified Cardinality & \ding{55} & $\checkmark$ \\
		*Exact Unqualified Cardinality & $\checkmark$ & $\checkmark$ \\
		*Exact Qualified Cardinality & $\checkmark$ & $\checkmark$ \\
		*Transitive Object Properties & $\checkmark$ & $\checkmark$ \\
		Context-Sp. Exclusive OR of P. & \ding{55} & \ding{55} \\
		Context-Sp. Exclusive OR of P. Groups & \ding{55} & \ding{55} \\	
		Allowed Values & \ding{55} & \ding{55} \\
		Not Allowed Values & \ding{55} & \ding{55} \\
		Literal Ranges & \ding{55} & \ding{55} \\
		Negative Literal Ranges & \ding{55} & \ding{55} \\
		Required Properties & $\checkmark$ & $\checkmark$ \\
		Optional Properties & \ding{55} & \ding{55} \\
		Repeatable Properties & $\checkmark$ & \ding{55} \\
		Negative Property Constraints & \ding{55} & $\checkmark$ \\
		*Individual Equality & $\checkmark$ & \ding{55} \\
		*Functional Properties & $\checkmark$ & $\checkmark$ \\
		*Inverse-Functional Properties & $\checkmark$ & $\checkmark$ \\
		*Value Restrictions & $\checkmark$ & $\checkmark$ \\
		*Self Restrictions & $\checkmark$ & $\checkmark$ \\
    \bottomrule
    \end{tabular}
		\label{tab:evaluation-cwa-una-dependency-1}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lcc@{}}
           & \multicolumn{2}{c}{\textbf{Dependency}}
    \\  \cmidrule{2-3}
    \\       \textbf{Constraint Types}
           & \rot{\emph{CWA}}
           & \rot{\emph{UNA}}
    \\ \midrule
		Primary Key Properties & $\checkmark$ & $\checkmark$ \\
		*Class-Specific Property Range & $\checkmark$ & \ding{55} \\
		*Class-Sp. Reflexive Object P. & $\checkmark$ & $\checkmark$ \\
		Membership in Controlled Vocabularies & $\checkmark$ & $\checkmark$ \\
		IRI Pattern Matching & \ding{55} & \ding{55} \\
		Literal Value Comparison & \ding{55} & \ding{55} \\
		Define Order & $\checkmark$ & $\checkmark$ \\
		Validation Levels & $\checkmark$ & $\checkmark$ \\
		String Operations & \ding{55} & \ding{55} \\
		Context-Specific Valid Classes & \ding{55} & $\checkmark$ \\
		Context-Specific Valid Properties & \ding{55} & $\checkmark$ \\
		Default Values* & $\checkmark$ & $\checkmark$ \\
		Mathematical Operations & \ding{55} & \ding{55} \\
		Language Tag Matching & $\checkmark$ & $\checkmark$ \\
		Language Tag Cardinality & $\checkmark$ & $\checkmark$ \\
		Whitespace Handling & \ding{55} & \ding{55} \\
		HTML Handling & \ding{55} & \ding{55} \\
		Conditional Properties & $\checkmark$ & $\checkmark$ \\
		Recommended Properties & $\checkmark$ & $\checkmark$ \\
		Handle RDF Collections & \ding{55} & \ding{55} \\
		Value is Valid for Datatype & \ding{55} & \ding{55} \\
		*Exploiting Class/Property Specialization Ontology Axioms & \ding{55} & $\checkmark$ \\
		*Cardinality Shortcuts & $\checkmark$ & $\checkmark$ \\ 
		Aggregations & \ding{55} & \ding{55} \\

		Class-Specific Irreflexive Object Properties* & \ding{55} & $\checkmark$ \\
		Provenance & $\checkmark$ & $\checkmark$ \\ 
		Data Model Consistency & $\checkmark$ & $\checkmark$ \\ 
		Structure & $\checkmark$ & $\checkmark$ \\  
		Labeling and Documentation & $\checkmark$ & $\checkmark$ \\ 
		Vocabulary & $\checkmark$ & \ding{55} \\
		HTTP URI Scheme Violation & \ding{55} & \ding{55} \\
    \bottomrule
    \end{tabular}
		\label{tab:evaluation-cwa-una-dependency-2}
    \end{center}
\end{table}

>>>>

\subsection{Class-Specific Irreflexive Object Properties}

@@

\ms{Ordering} corresponds to the requirements
\ms{R-121-SPECIFY-ORDER-OF-RDF-} \ms{RESOURCES} and
\ms{R-217-DEFINE-ORDER-FOR-FORMS/DISPLAY}.
With this constraint objects of object properties can be ordered as well as literals of data properties and objects of object properties.

@@

\section{Default Values}

@@

*Property Domains & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
*Property Ranges & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\

@@

*Existential Quantifications & \ding{55} & $\checkmark$ & \ding{55} & $\sim$ & $\sim$ & $\checkmark$ \\
*Universal Quantifications & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\

@@

*Primary Key Properties & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\

@@

Ordering & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\

@@

\begin{evaluation-overall}
Context-Specific Valid Classes & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Context-Specific Valid Properties & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
*Default Values & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ & \ding{55} & $\checkmark$ \\
Mathematical Operations & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Language Tag Matching & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Language Tag Cardinality & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Whitespace Handling & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
HTML Handling & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Conditional Properties & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Recommended Properties & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Handle RDF Collections & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Value is Valid for Datatype & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Use Sub-Super Relations in Validation & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
*Cardinality Shortcuts & \ding{55} & $\checkmark$ & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
Aggregations & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\

*Class-Specific Irreflexive Object Properties & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Provenance & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Data Model Consistency & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Structure & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\  
Labeling and Documentation & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Vocabulary & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
HTTP URI Scheme Violation & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
\end{evaluation-overall}

@@

*Property Domains & $\checkmark$ & $\sim$ & $\checkmark$ \\ 
*Property Ranges & $\checkmark$ & $\sim$ & $\checkmark$ \\ 

@@

*Existential Quantifications & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
*Universal Quantifications & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  

@@

*Primary Key Properties & $\checkmark$ & $\sim$ & $\checkmark$ \\ 

@@

Ordering & $\checkmark$ & $\checkmark$ & \ding{55} \\ 

@@

\begin{evaluation-generic}
Context-Specific Valid Classes & \ding{55} & $\checkmark$ & \ding{55} \\   
Context-Specific Valid Properties & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
*Default Values & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
Mathematical Operations & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
Language Tag Matching & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
Language Tag Cardinality & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
Whitespace Handling & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
HTML Handling & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
Conditional Properties & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
Recommended Properties & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
Handle RDF Collections & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
Value is Valid for Datatype & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
Use Sub-Super Relations in Validation & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
*Cardinality Shortcuts & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
Aggregations & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
*Class-Specific Irreflexive Object Properties & & & \\
Provenance & & & \\
Data Model Consistency & & & \\
Structure & & & \\  
Labeling and Documentation & & & \\
Vocabulary & & & \\
HTTP URI Scheme Violation & & & \\
\end{evaluation-generic}

@@

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lcc@{}}
           & \multicolumn{2}{c}{\textbf{Dependency}}
    \\  \cmidrule{2-3}
    \\       \textbf{Constraint Types}
           & \rot{\emph{CWA}}
           & \rot{\emph{UNA}}
    \\ \midrule
		*Subsumption & $\checkmark$ & $\checkmark$ \\
		*Class Equivalence & $\checkmark$ & $\checkmark$ \\
		*Sub Properties & $\checkmark$  & $\checkmark$ \\
		*Property Domains & $\checkmark$ & $\checkmark$ \\
		*Property Ranges & $\checkmark$ & $\checkmark$ \\
		*Inverse Object Properties & $\checkmark$ & $\checkmark$ \\
		*Symmetric Object Properties & $\checkmark$ & $\checkmark$ \\
		*Asymmetric Object Properties & \ding{55} & \ding{55} \\
		*Reflexive Object Properties & $\checkmark$ & $\checkmark$ \\
		*Irreflexive Object Properties & \ding{55} & \ding{55} \\
		Disjoint Properties & \ding{55} & \ding{55} \\
		Disjoint Classes & \ding{55} & $\checkmark$ \\
		Context-Sp. Property Groups & $\checkmark$ & $\checkmark$ \\
		Context-Sp. Inclusive OR of P. & $\checkmark$ & $\checkmark$ \\
		Context-Sp. Inclusive OR of P. Groups & $\checkmark$ & $\checkmark$ \\
		Recursive Queries & \ding{55} & \ding{55} \\
		Individual Inequality & \ding{55} & \ding{55} \\
		*Equivalent Properties & $\checkmark$ & $\checkmark$ \\
		Property Assertions & $\checkmark$ & $\checkmark$ \\
		Data Property Facets & \ding{55} & \ding{55} \\
		Literal Pattern Matching & \ding{55} & \ding{55} \\
		Negative Literal Pattern Matching & \ding{55} & \ding{55} \\
		*Object Property Paths & $\checkmark$ & $\checkmark$ \\
		*Intersection & $\checkmark$ & $\checkmark$ \\
		*Disjunction & $\checkmark$ & $\checkmark$ \\
		*Negation & \ding{55} & \ding{55} \\
		*Existential Quantifications & $\checkmark$ & $\checkmark$ \\
		*Universal Quantifications & \ding{55} & $\checkmark$ \\
		*Minimum Unqualified Cardinality & $\checkmark$ & $\checkmark$ \\
		*Minimum Qualified Cardinality & $\checkmark$ & $\checkmark$ \\
		*Maximum Unqualified Cardinality & \ding{55} & $\checkmark$ \\
		*Maximum Qualified Cardinality & \ding{55} & $\checkmark$ \\
		*Exact Unqualified Cardinality & $\checkmark$ & $\checkmark$ \\
		*Exact Qualified Cardinality & $\checkmark$ & $\checkmark$ \\
		*Transitive Object Properties & $\checkmark$ & $\checkmark$ \\
		Context-Sp. Exclusive OR of P. & \ding{55} & $\checkmark$ \\
		Context-Sp. Exclusive OR of P. Groups & \ding{55} & $\checkmark$ \\	
		Allowed Values & \ding{55} & $\checkmark$ \\
		Not Allowed Values & \ding{55} & $\checkmark$ \\
		Literal Ranges & \ding{55} & \ding{55} \\
		Negative Literal Ranges & \ding{55} & \ding{55} \\
		Required Properties & $\checkmark$ & $\checkmark$ \\
		Optional Properties & \ding{55} & \ding{55} \\
		Repeatable Properties & $\checkmark$ & \ding{55} \\
		Negative Property Constraints & \ding{55} & $\checkmark$ \\
		*Individual Equality & $\checkmark$ & \ding{55} \\
		*Functional Properties & $\checkmark$ & $\checkmark$ \\
		*Inverse-Functional Properties & $\checkmark$ & $\checkmark$ \\
		*Value Restrictions & $\checkmark$ & $\checkmark$ \\
		*Self Restrictions & $\checkmark$ & $\checkmark$ \\
    \bottomrule
    \end{tabular}
		\label{tab:evaluation-cwa-una-dependency-1}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lcc@{}}
           & \multicolumn{2}{c}{\textbf{Dependency}}
    \\  \cmidrule{2-3}
    \\       \textbf{Constraint Types}
           & \rot{\emph{CWA}}
           & \rot{\emph{UNA}}
    \\ \midrule
		*Primary Key Properties & $\checkmark$ & $\checkmark$ \\
		*Class-Specific Property Range & $\checkmark$ & $\checkmark$ \\
		*Class-Sp. Reflexive Object P. & $\checkmark$ & $\checkmark$ \\
		Membership in Controlled Vocabularies & $\checkmark$ & $\checkmark$ \\
		IRI Pattern Matching & \ding{55} & $\checkmark$ \\
		Literal Value Comparison & \ding{55} & \ding{55} \\
		Ordering & $\checkmark$ & \ding{55} \\
		Validation Levels & $\checkmark$ & \ding{55} \\
		String Operations & \ding{55} & \ding{55} \\
		Context-Specific Valid Classes & \ding{55} & \ding{55} \\
		Context-Specific Valid Properties & \ding{55} & \ding{55} \\
		*Default Values & $\checkmark$ & $\checkmark$ \\
		Mathematical Operations & \ding{55} & \ding{55} \\
		Language Tag Matching & $\checkmark$ & \ding{55} \\
		Language Tag Cardinality & $\checkmark$ & $\checkmark$ \\
		Whitespace Handling & \ding{55} & \ding{55} \\
		HTML Handling & \ding{55} & \ding{55} \\
		Conditional Properties & $\checkmark$ & $\checkmark$ \\
		Recommended Properties & $\checkmark$ & $\checkmark$ \\
		Handle RDF Collections & \ding{55} & \ding{55} \\
		Value is Valid for Datatype & \ding{55} & \ding{55} \\
		Use Sub-Super Relations in Validation & \ding{55} & $\checkmark$ \\
		*Cardinality Shortcuts & $\checkmark$ & $\checkmark$ \\ 
		Aggregations & \ding{55} & \ding{55} \\
		*Class-Specific Irreflexive Object Properties & \ding{55} & $\checkmark$ \\
		Provenance & $\checkmark$ & $\checkmark$ \\ 
		Data Model Consistency & $\checkmark$ & $\checkmark$ \\ 
		Structure & $\checkmark$ & $\checkmark$ \\  
		Labeling and Documentation & $\checkmark$ & $\checkmark$ \\ 
		Vocabulary & $\checkmark$ & $\checkmark$ \\
		HTTP URI Scheme Violation & \ding{55} & $\checkmark$ \\
    \bottomrule
    \end{tabular}
		\label{tab:evaluation-cwa-una-dependency-2}
    \end{center}
\end{table}
